Supplementary materials to: Describing vocalizations in young children: A big data approach through citizen science annotations

### 2021-03-23 202010_jslhr/paper.Rmd
switched to renv

```{r setup, include = FALSE}

library(groundhog)
groundhog.day="2021-02-23"
#groundhog.library('papaja', groundhog.day) #NOTE! THIS IS A POINT OF POTENTIAL NON-REPRODUCIBILITY
library(papaja) #NOTE!
groundhog.library('tidyverse', groundhog.day)
groundhog.library('dplyr', groundhog.day)
groundhog.library('ggplot2', groundhog.day)
groundhog.library('rmarkdown', groundhog.day)
groundhog.library('caret', groundhog.day)
groundhog.library('scales', groundhog.day)
groundhog.library('kableExtra', groundhog.day)
groundhog.library('rel', groundhog.day)
groundhog.library('ggpubr', groundhog.day)
groundhog.library('lme4', groundhog.day)
groundhog.library('e1071', groundhog.day)

@@

read.csv(".chunks_maj_judgments.csv")->chunks

>>>>

```{r setup, include = FALSE}
library(rel)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(lme4)
library(e1071)
library(papaja)
library(caret)
library(scales)
library(kableExtra)

@@

read.csv("chunks_maj_judgments.csv")->chunks

### 2021-03-23 202010_jslhr/sup_mat.Rmd
switched to renv

```{r setup, include=FALSE}
library(groundhog)
groundhog.day="2021-02-23"
groundhog.library('tidyverse', groundhog.day)
groundhog.library('dplyr', groundhog.day)
groundhog.library('ggplot2', groundhog.day)
groundhog.library('rmarkdown', groundhog.day)
groundhog.library('caret', groundhog.day)
groundhog.library('scales', groundhog.day)
groundhog.library('kableExtra', groundhog.day)
groundhog.library('rel', groundhog.day)
groundhog.library('ggpubr', groundhog.day)
groundhog.library('lme4', groundhog.day)
groundhog.library('e1071', groundhog.day)
groundhog.library('rjson', groundhog.day)

>>>>

```{r setup, include=FALSE}
library('tidyverse')
library('dplyr')
library('ggplot2')
library('rmarkdown')
library('caret')
library('scales')
library('kableExtra')
library('rel')
library('ggpubr')
library('lme4')
library('e1071')
library('rjson')
